Active Learning Benchmark

### 2023-01-30 doc/research_presentation/research_presentation.tex
dna runs
docs

\begin{frame}[fragile]{Scope}
	The framework is planned to include
	\begin{itemize}
		\item Three different domains (Tabular, Image, Text)
		\item SOTA baseline methods 
		\item Preprocessed datasets (train/test split and seed set)
		\item Tuned classifiers for each dataset
		\item Set logging and evaluation procedures
		\item (Single Domain and Domain Transfer use cases)
	\end{itemize}
	The framework will \textbf{not} include
	\begin{itemize}
		\item Batch Active Learning
	\end{itemize}
\end{frame}

@@

@@

@@

\begin{frame}[fragile]{Hyperparameters}
	Data HPs are fixed by the dataset (budget, seed set, ...)

@@

>>>>

\begin{frame}[fragile]{Scope}
	The framework is planned to include
	\begin{itemize}
		\item Three different domains (Tabular, Image, Text)
		\item SOTA baseline methods 
		\item Preprocessed datasets (train/test split and seed set)
		\item Tuned classifiers for each dataset
		\item Set logging and evaluation procedures
		\item (Single Domain and Domain Transfer use cases)
	\end{itemize}
	The framework will \textbf{not} include
	\begin{itemize}
		\item Batch Active Learning
		\item Elaborate Training (Data Augmentation, etc.)
	\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Dataset Potential}
	\begin{figure}
		\centering
		\includegraphics[width=0.7\linewidth]{pics/splice_oracle.png}
	\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Cross Validation}
	\begin{columns}
		\begin{column}{0.5\linewidth}
			Random Sampling
			\includegraphics[width=\linewidth]{pics/splice_random_convergence.jpg}
		\end{column}
		\hspace{3mm}
		\begin{column}{0.5\linewidth}
			Uncertainty Sampling
			\includegraphics[width=\linewidth]{pics/splice_margin_convergence.jpg}
		\end{column}
	\end{columns}
\end{frame}

@@

\begin{frame}[fragile]{Cross Validation}
	\begin{figure}
		\centering
		\includegraphics[width=.7\linewidth]{pics/splice_margin100_convergence.jpg}
	\end{figure}
\end{frame}

\begin{frame}[fragile]{Hyperparameters}
	Data HPs are fixed for each dataset (budget, seed set, ...)

@@

\begin{frame}[fragile]{The End}
	Cheers
\end{frame}

\begin{frame}[fragile]{Classifier Training}
	Labeled points are unweighted

	Always at least one epoch of training

	Aggressive early stopping with patience $0$

	Adam (NAdam) optimizer, since SGD proves to be too slow (needs more epochs)
\end{frame}
